---
title: "Covariation-ContinuousVariables"
author: "Anisha BharathSingh"
date: "6/13/2019"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Install and load tidyverse
```{r, install, load tidyvers}
install.packages("tidyverse") 
library(tidyverse)
install.packages("ggrepel")
library(ggrepel)
```

## Read CSV
```{r, read csv, variables names }
WorldHappinessData <- read_csv("HappinessData.csv") 
head(WorldHappinessData) #preview data
```
## Rename Variables
```{r, rename}
colnames(WorldHappinessData) <- c("Country", "Year", "Ladder", "Log_of_GDP_per_capita", "Social_support", "Health_life_expectancy", "Freedom", "Generosity", "Corruption", "Positive_affect", "Negative_affect")
colnames(WorldHappinessData) #print data frame variable names
```

## Create 2017 Data Frame
```{r}
WorldHappinessData2017 <- filter(WorldHappinessData, Year == "2017") #filter data set to only include observations where Year = 2017
```


## Scatterplot of Freedom and Positive Emotion
```{r}
  ggplot(data = WorldHappinessData2017, mapping = aes(x= Freedom, y= Positive_affect)) +
  geom_point() + #scatteplot
  geom_smooth() + #line plot
  ggtitle("Freedom vs. Positive Emotion 2017") + 
  labs(y = "Positive Emotion")
```  

## Create Happiest Countries Data Frame
```{r}
HappyCountries <- filter(WorldHappinessData2017, Positive_affect > 0.8) #filter data set to only include observations where positive affect is greater than 0.8
```

## Scatterplot of Top Positive Emotions Countries with Labels
```{r}
  ggplot(HappyCountries, aes(x= Freedom, y= Positive_affect, label=Country))+
  geom_point() +
  geom_label_repel(aes(label = Country), #add data point labels
                  box.padding   = 0.35, 
                  point.padding = 0.5,
                  segment.color = 'grey50') +
  theme_classic() +
  ggtitle("Freedom vs. Top Positive Countries in 2017") + 
  labs(y = "Positive Emotion")
```

## ## Create Saddest Countries Data Frame
```{r}
SadCountries <- filter(WorldHappinessData2017, Positive_affect < 0.5) #filter data set to only include observations where positive affect is less than 0.5
```

## Scatterplot of Bottom Positive Emotions Countries with Labels
```{r}
  ggplot(SadCountries, aes(x= Freedom, y= Positive_affect, label=Country))+
  geom_point() +
  geom_label_repel(aes(label = Country), #add data point labels
                  box.padding   = 0.35, 
                  point.padding = 0.5,
                  segment.color = 'grey50') +
  theme_classic() +
  ggtitle("Freedom vs. Bottom Positive Countries in 2017") + 
  labs(y = "Positive Emotion")
```


## Create Bottom 3 Country Data Frame
```{r}
Bottom3Countries <- filter(WorldHappinessData, Country == "Tunisia" | Country == "Turkey" | Country == "Yemen" ) #create data frame that only hace data for the bottom 3 countries
```

## Create Facet Plot of Time Series Data for Freedom and Positive Emotion for the Bottom 3 Countries
```{r}
ggplot(data = Bottom3Countries) +
  geom_smooth(mapping = aes(x= Year, y= Positive_affect)) +
  geom_smooth(mapping = aes(x= Year, y= Freedom), color = "red") +
  facet_grid(~Country) + #facet by country
  ggtitle("Freedom and Positive Emotion for the Bottom Three Countries (2005-2017)") + 
  labs(y = "Positive Emotion") +
  theme(axis.text.x  = element_text(angle=60, vjust=0.5, size=8)) #angle x-axis labels
  
``` 


