---
title: "ggplot2 geom_point() shapes + colors"
author: "Anisha BharathSingh"
date: "5/16/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#load packages
```{r}
library("ggplot2")
library("dplyr")
```

#import data
```{r import}
worldHappiness <- read.csv("2015.csv")
```

# omit incomplete observations if any
```{r}
na.omit(worldHappiness)
```

#examine column names
```{r pressure, echo=FALSE}
colnames(worldHappiness)
```


#filter for specific regions
```{r}
happinessRegions <- filter(worldHappiness, Region == "Middle East and Northern Africa" | Region == "Central and Eastern Europe" | Region == "Western Europe" | Region == "Sub-Saharan Africa")

```


# Scatterplot with geom_point()
```{r}
ggplot(happinessRegions, aes(Freedom, Happiness.Score)) +
  geom_point() +
  theme_minimal() +
  ggtitle("Freedom vs. Happiness (2015)") + 
  labs(x = "Freedom", y = "Happiness Score")
```

# Scatterplot with geom_point()
# color by Region
```{r}
ggplot(happinessRegions, aes(Freedom, Happiness.Score)) +
  geom_point(aes(color = Region)) +
  theme_minimal() +
  ggtitle("Freedom vs. Happiness (2015)") + 
  labs(x = "Freedom", y = "Happiness Score")
```

# Scatterplot with geom_point() 
# color and shape by Region
```{r}
ggplot(happinessRegions, aes(Freedom, Happiness.Score)) +
  geom_point(aes(color = Region, shape = Region)) +
  theme_minimal() +
  ggtitle("Freedom vs. Happiness (2015)") + 
  labs(x = "Freedom", y = "Happiness Score")
```

# # Scatterplot with geom_point() 
# color and shape by Region
# set individual shapes
```{r}
ggplot(happinessRegions, aes(Freedom, Happiness.Score)) +
  geom_point(aes(shape = Region, color = Region)) +
  theme_minimal() +
  ggtitle("Freedom vs. Happiness (2015)") + 
  labs(x = "Freedom", y = "Happiness Score") +
  scale_shape_manual(values = c(5, 7, 10, 13))
```

# # Scatterplot with geom_point() 
# color and shape by Region
# set individual shapes + colors
```{r}
ggplot(happinessRegions, aes(Freedom, Happiness.Score)) +
  geom_point(aes(shape = Region, color = Region)) +
  theme_minimal() +
  ggtitle("Freedom vs. Happiness (2015)") + 
  labs(x = "Freedom", y = "Happiness Score") +
  scale_shape_manual(values = c(5, 7, 10, 13)) +
  scale_color_manual(values = c("#C97B84", "#A5D8FF", "#9CC4B2", "#9532a8"))
```



