---
title: "Democratic Candidates on Twitter"
author: "Anisha BharathSingh"
date: "11/24/2019"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Install Packages
```{r}
#install.packages("stringr")
#install.packages("twitteR")
#install.packages("purrr")
#install.packages("tidytext")
#install.packages("dplyr")
#install.packages("tidyr")
#install.packages("lubridate")
#install.packages("scales")
#install.packages("broom")
#install.packages("ggplot2")
```

## Load packages
```{r}
library(stringr)
library(twitteR)
library(purrr)
library(tidytext)
library(dplyr)
library(tidyr)
library(lubridate)
library(scales)
library(broom)
library(ggplot2)
```

## Access keys and tokens
```{r}
api_Key = "Insert Here"
api_Secret = "Insert Here"
access_Token = "Insert Here"
access_Token_Secret = "Insert Here"
```


## Setup R and Twitter API Connection
```{r}
options(httr_oauth_cache=TRUE)
setup_twitter_oauth(consumer_key = api_Key, consumer_secret = api_Secret,
access_token = access_Token, access_secret = access_Token_Secret)
```


## Extract tweets for Biden
```{r}
JoeBiden <- userTimeline("JoeBiden", n = 500, includeRts=TRUE,  excludeReplies=FALSE)
JoeBiden_df <- twListToDF(JoeBiden)
head(JoeBiden_df)
```
## Extract tweets for Sanders
```{r}
BernieSanders <- userTimeline("BernieSanders", n = 500, includeRts=TRUE,  excludeReplies=FALSE)
BernieSanders_df <- twListToDF(BernieSanders)
head(BernieSanders_df)
```
## Extract tweets for Warren
```{r}
ElizabethWarren <- userTimeline("ewarren", n = 500, includeRts=TRUE,  excludeReplies=FALSE)
ElizabethWarren_df <- twListToDF(ElizabethWarren)
head(ElizabethWarren_df)
```
## Extract tweets for Buttigieg
```{r}
PeteButtigieg <- userTimeline("PeteButtigieg", n = 500, includeRts=TRUE,  excludeReplies=FALSE)
PeteButtigieg_df <- twListToDF(PeteButtigieg)
head(PeteButtigieg_df)
```
## Extract tweets for Harris
```{r}
KamalaHarris <- userTimeline("KamalaHarris", n = 500, includeRts=TRUE,  excludeReplies=FALSE)
KamalaHarris_df <- twListToDF(KamalaHarris)
head(KamalaHarris_df)
```
## Extract tweets for Yang
```{r}
AndrewYang <- userTimeline("AndrewYang", n = 500, includeRts=TRUE,  excludeReplies=FALSE)
AndrewYang_df <- twListToDF(AndrewYang)
head(AndrewYang_df)
```

## Create new data frame
```{r}
DemsTweets <- rbind(JoeBiden_df, BernieSanders_df, ElizabethWarren_df, PeteButtigieg_df, KamalaHarris_df, AndrewYang_df)
write.csv(DemsTweets, "DemCandidateTweets.csv")
```

## Take a look at Variables
```{r}
colnames(DemsTweets)
```


## Explore Original Tweet vs Retweet Frequency
```{r}
Retweets <- DemsTweets %>%
  select(screenName, isRetweet)
  
Retweets$isRetweet = ifelse(Retweets$isRetweet == 'FALSE', 'Original Tweets', 'Retweets')

Retweets = Retweets %>% 
  group_by(isRetweet, screenName) %>%
  summarize(n=n())

```

## Plot Bar Plot of Original Tweets and Retweets
```{r}
ggplot(Retweets, aes(x = screenName, y = n, fill = isRetweet)) + geom_bar(stat = 'identity') + ggtitle("Original Tweets vs. Retweets Per Candidate") + labs(y = "Count", x = "Candidate", fill = "Legend") + scale_x_discrete(labels=c("Andrew Yang", "Bernie Sanders", "Elizabeth Warren", "Joe Biden", "Kamala Harris", "Pete Buttigieg"))
```


## How many tweets have candidates replied to?
```{r}
TweetReplies = DemsTweets %>%
  select(screenName, replyToSN)

TweetReplies$replyToSN  = ifelse(TweetReplies$replyToSN == ' ', NA, TweetReplies$replyToSN)

TweetReplies = na.omit(TweetReplies)

TweetReplies = TweetReplies %>% 
  group_by(screenName) %>%
  summarize(n=n())
```

## Bar Plot of Number of tweets candidate replied to
```{r}
ggplot(TweetReplies, aes(x = screenName, y = n)) + geom_bar(stat = 'identity', fill = "LightBlue") + ggtitle("Number of Tweets Candidates Replied To") + labs(y = "Count", x = "Candidate") + scale_x_discrete(labels=c("Andrew Yang", "Bernie Sanders", "Elizabeth Warren", "Joe Biden", "Kamala Harris", "Pete Buttigieg"))
```

```{r}
colnames(TweetReplies)
```

## Top handles that got replied to
```{r}
RepliedTo = DemsTweets %>%
  select(screenName, replyToSN)

RepliedTo = na.omit(RepliedTo)

RepliedTo = RepliedTo %>% 
  group_by(screenName, replyToSN) %>%
  summarize(n=n())

Biden = RepliedTo %>%
  filter(screenName=="JoeBiden") %>%
  arrange(desc(n))
Sanders = RepliedTo %>%
  filter(screenName=="BernieSanders") %>%
  arrange(desc(n))
Warren = RepliedTo %>%
  filter(screenName=="ewarren") %>%
  arrange(desc(n))
Buttigieg = RepliedTo %>%
  filter(screenName=="PeteButtigieg") %>%
  arrange(desc(n))
Harris = RepliedTo %>%
  filter(screenName=="KamalaHarris") %>%
  arrange(desc(n))
Yang = RepliedTo %>%
  filter(screenName=="AndrewYang") %>%
  arrange(desc(n))

Biden
Sanders
Warren
Buttigieg
Harris
Yang

```


## How many favorites do candidates original tweets get?
```{r}
FavoritedTweets = DemsTweets %>%
  filter(DemsTweets$isRetweet == 'FALSE') %>%
  select(screenName, favoriteCount)

AverageFavorite <- FavoritedTweets %>%
  mutate() %>%
  group_by(screenName) %>%
  summarize(AverageFavorites = (sum(favoriteCount)/length(favoriteCount)))

AverageFavorite
```

## Plot of average favorites for candidates tweets
```{r}
ggplot(AverageFavorite, aes(x = screenName, y = AverageFavorites)) + geom_bar(stat = 'identity', fill = "lightblue") + ggtitle("Average Number of Favorites for Candidate's Tweets") + labs(y = "Count", x = "Candidate") +  scale_x_discrete(labels=c("Andrew Yang", "Bernie Sanders", "Elizabeth Warren", "Joe Biden", "Kamala Harris", "Pete Buttigieg"))
```


## How many retweets do candidates original tweets get
```{r}
NumberOfRetweets = DemsTweets %>%
  filter(DemsTweets$isRetweet == 'FALSE') %>%
  select(screenName, retweetCount)
  
AverageNumberOfRetweets <- NumberOfRetweets %>% 
  mutate() %>%
  group_by(screenName) %>%
  summarize(AverageRetweets = (sum(retweetCount)/length(retweetCount)))

AverageNumberOfRetweets
```

## Plot of average number of retweets for candidates tweets
```{r}
ggplot(AverageNumberOfRetweets, aes(x = screenName, y = AverageRetweets)) + geom_bar(stat = 'identity', fill = "lightblue") + ggtitle("Average Number of Retweets of Candidate's Tweets") + labs(y = "Count", x = "Candidate") +  scale_x_discrete(labels=c("Andrew Yang", "Bernie Sanders", "Elizabeth Warren", "Joe Biden", "Kamala Harris", "Pete Buttigieg"))
```
