---
title: "Google Trends COVID-19 Data 2020"
author: "Anisha BharathSingh"
date: "12/30/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Install packages
```{r install packages}
install.packages("gtrendsR")
install.packages("magrittr")
install.packages("dplyr")
```

#Load packages
```{r load packages}
library(gtrendsR)
library(magrittr)
library(dplyr)
```
#Retrieve data for "covid" and "coronavirus" with gtrends()
```{r}
res <- gtrends(c("covid", "coronavirus"), geo = "US", time = "2020-01-01 2020-12-29")
```

#Plot search interest over time for "covid" vs "coronavirus"
```{r}
plot(res)
```

#Find top 5 related queries for "coronavirus" and "covid"
```{r}
rel <- res$related_queries %>%
  group_by(keyword) %>%
  filter(related_queries == "top") %>% #remove queries in breakouts
  mutate(search_interest = as.numeric(subject)) %>% #convert search interest to numeric
  top_n(5,search_interest) %>% #keep top 5 by search interest only
  arrange(desc(search_interest)) #arrange in descending order

#reorder columns
rel <- rel[ ,c("search_interest", "related_queries", "value", "geo", "keyword", "category", "subject")]

#print update data table
print(rel)
```

#Retrieve and plot data for "coronavirus" and related queries with gtrends()
```{r}
res_coronavirus <- gtrends(c("coronavirus", "coronavirus cases", "coronavirus update", "us coronavirus"), geo = "US", time = "2020-01-01 2020-12-29")
plot(res_coronavirus)
```


#Retrieve and plot data for "coronavirus" and related queries with gtrends()
```{r}
res_covid <- gtrends(c("covid", "covid 19", "covid cases", "covid testing"), geo = "US", time = "2020-01-01 2020-12-29")
plot(res_covid)
```

#Retrieve and plot data for "coronavirus vaccine" vs "covid vaccine" with gtrends()
```{r}
res_vaccine <- gtrends(c("covid vaccine", "coronavirus vaccine"), geo = "US", time = "2020-01-01 2020-12-29")
plot(res_vaccine)
```



