---
title: "A/B Testing"
author: "Anisha BharathSingh"
date: "6/26/2020"
output: word_document
---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#install.packages("readxl")
library(readxl)
#install.packages("ggplot2")
library(ggplot2)
install.packages("tidyverse", type = "binary")
library(tidyverse)
#install.packages("lubridate")
library(lubridate)
#install.packages("WebPower")
library(WebPower)
#install.packages("broom")
library(broom)
```

#Read in baseline data + view column names
```{r}
baselineData <- read_excel("BaselineDataset.xlsx")
head(baselineData)
```

#Coerce to Date variable from POSIXct to Date with as.Date from the lubridate package
```{r}
baselineData$Date <- as.Date(baselineData$Date)
head(baselineData)
```

#take a look at number of conversions throughout the year
```{r}
baselineDataWeek <- baselineData %>%
  group_by(week(Date)) %>%
  summarize(conversion = mean(TotalConversions))
```

# Build plot in ggplot to look at average converions by week
```{r}
ggplot(baselineDataWeek, aes(x = `week(Date)`,
                           y = `conversion` )) +
  geom_point() +
  geom_line() +
  scale_y_continuous(limits = c(0, 30)) +
  ggtitle("Average Conversions for 'the KeepKool' Product Page by Week (2019)") +
  labs(y = "Number of Conversions", x = "Week Number")
```

#Get data for May
```{r}
baselineDataMay <- subset(baselineData, Date > "2019-05-01" & Date < "2019-05-31")
```

# Power analysis 
# first get averages for wp.poisson function
```{r}  
baselineDataMayAverages <- baselineDataMay %>%
  summarize(conversionMonthControl = mean(ConversionsControl), conversionMonthAlternate = mean(ConversionsAlternate))
baselineDataMayAverages
```

#percent increase
```{r}
(8.689655 - 4.758621)/4.758621
```

#wp.poisson for sample size
```{r}
wp.poisson(n = NULL, 
           exp0 = 4.758621, 
           exp1 = 0.8260868, 
           alpha = 0.05,
           power = 0.8, 
           alternative = "two.sided",
           family = "Poisson", 
           parameter = 1)
```
#65 points needed per condition


#load experiment data
```{r}
ExperimentData <- read_excel("ExperimentData.xlsx")
ExperimentData$Date <- as.Date(ExperimentData$Date)
head(ExperimentData)
```

#put conditions in own column
```{r}
experimentData <- gather(ExperimentData, key = "Condition", value = "Conversions",
       Control, Experiment)
```

#find means and variances (will need variance later)
```{r}
experimentData %>%
  group_by(Condition) %>%
  summarize(conversionMean = mean(Conversions), conversionVar = var(Conversions))
```

#plot to see difference between control and experiment
```{r}
ggplot(experimentData, aes(x = Date, y = Conversions, group = Condition, col = Condition)) +
  geom_point() +
  geom_line() +
  ggtitle("Control vs. Experiment Webpage Conversions (May-July 2020)") +
  labs(y = "Number of Conversions")
```

#use glm regression 
#use poisson because its discrete data
#use quasi poisson because means do not equal variance
```{r}
glm(Conversions ~ Condition, family = "quasipoisson", data = experimentData) %>%
  tidy()
```




