---
title: "TF-IDF for SEO with R"
author: "Anisha BharathSingh"
date: "3/23/2020"
output: pdf_document
---

#Setup 
```{r setup, include=FALSE}
#install.packages('rvest')
#install.packages('tm')
#install.packages('corpus')
#install.packages('ggplot2')
#install.packages('tidytext')
#install.packages('textdata')
#install.packages('dplyr')
#install.packages('tidyverse')
```

```{r}
library(rvest)
library(tm)
library(corpus)
library(ggplot2)
library(tidytext)
library(textdata)
library(dplyr)
library(tidyverse)
```

## Step 1: Scrape Text from Webpages

#Import Text from Journey to Data Scientist 
```{r}
#Create the URL variable for desired webpage to be scraped
url <- 'https://journeytodatascientist.blog/2020/02/02/data-science-pioneers-conquering-the-next-frontier/'

#Reading the webpage HTML code and specific nodes (information) wanted from the webpage
webpage <- read_html(url)
jtds <- html_nodes(webpage,'.entry-content')

#Converting nodes to text
jtds <- html_text(jtds)
```

#Import Text from Dataiku
```{r}
#Create the URL variable for desired webpage to be scraped
url <- 'https://pages.dataiku.com/data-science-documentary'

#Reading the webpage HTML code and specific nodes (information) wanted from the webpage
webpage <- read_html(url)
di <- html_nodes(webpage,'.body-container .row-number-2 .row-fluid')

#Converting nodes to text
di <- html_text(di)
```


#Import Text from Optimal BI
```{r}
#Create the URL variable for desired webpage to be scraped
url <- 'https://optimalbi.com/blog/2019/11/14/data-science-pioneers-movie/'

#Reading the webpage HTML code and specific nodes (information) wanted from the webpage
webpage <- read_html(url)
ob <- html_nodes(webpage,'p:nth-child(7) , p:nth-child(6) , .entry-content > p:nth-child(5) , .aligncenter~ p:nth-child(4) , .aligncenter+ p , #left-area p:nth-child(1)')

#Converting nodes to text
ob <- html_text(ob)
```



## Step 2: Create and Clean Corpus

# Create Corpus with 'Corpus' Package
```{r}
jtds <- as_corpus_frame(jtds)
di <- as_corpus_frame(di)
ob <- as_corpus_frame(ob)

```

# Clean & Prepare Corpii
```{r}
# Remove punctuation from corpus:
jtds <- term_stats(jtds, drop_punct = TRUE)
di <- term_stats(di, drop_punct = TRUE)
ob <- term_stats(ob, drop_punct = TRUE)

# Drop Column 3 
jtds <- jtds[,1:2]
di <- di[,1:2]
ob <- ob[,1:2]

# Rename column names
colnames(jtds) <- c("word", "count")
colnames(di) <- c("word", "count")
colnames(ob) <- c("word", "count")

```

## Step 3: Find "TF"

# add source, total count and then TF to each data frame 
```{r}
jtds <- jtds %>%
  mutate(source = "Journey to Data Scientist") %>%
  mutate(total_words = sum(jtds$count)) %>%
  mutate("TF" = count / total_words) 


di <- di %>%
  mutate(source = "Dataiku") %>%
  mutate(total_words = sum(di$count)) %>%
  mutate("TF" = count / total_words) 


ob <- ob %>%
  mutate(source = "Optimal BI") %>%
  mutate(total_words = sum(ob$count)) %>%
  mutate("TF" = count / total_words) 

```


## Step 4: Find "IDF" and "TF-IDF"
#combine data frames
```{r}
combined_dataframe <- rbind(jtds, di, ob)
combined_dataframe
```

#Remember:
#IDF = log(Total Number of Documents / number of documents with term x in it) 
#TF-IDF = TF * IDF

#find tf-idf
```{r}
tf_idf <- combined_dataframe %>% 
  add_count(word) %>%
  group_by(source) %>%
  mutate("IDF" = 1 + log(3 / n)) %>%
  mutate("TF_IDF" = TF * IDF) 
```


## Step 5: Analysis
#bar chart showing tf-idf for target keywords in comparison to top performing blogs
```{r}

words_target_keywords <- filter(tf_idf, word == "data" | word == "science" | word == "pioneers" | word == "documentary" | word == "artificial" | word == "intelligence" | word == "ai" | word == "machine" | word == "learning" | word == "scientists" | word == "dataiku" | word == "screening")

```
```{r}
ggplot(data = words_target_keywords, aes(x = reorder(word, -TF_IDF), y = TF_IDF, fill = source)) + 
  geom_bar(stat = "identity", position = "dodge") + 
  ggtitle("Comparison of TF-IDF for Target Keywords among Competitors") + 
  labs(x = "Keyword", y = "TF IDF Score") + 
  theme(axis.text.x  = element_text(angle=60, vjust=0.5, size=8)) + 
  theme(axis.title.y = element_text(size=10))
```




#bar chart showing keywords with highest tf-idf across blogs
```{r}
tf_idf_arrange <- arrange(tf_idf, desc(TF_IDF))
tf_idf_10 <- tf_idf_arrange[1:50, ]

ggplot(tf_idf_10, aes(x = reorder(word, -TF_IDF), y = TF_IDF, fill = source)) + 
  geom_bar(stat = "identity", position = "dodge") + 
  ggtitle("Keywords with the Highest TF-IDF Scores among Competitors") + 
  labs(x = "Keyword", y = "TF-IDF Score") + 
  theme(axis.text.x  = element_text(angle=60, vjust=0.5, size=8)) + 
  theme(axis.title.y = element_text(size=10))
```

